A Cross-Benchmark Comparison of Learning to Rank Methods

### 2014-05-16 cikm_paper/paper.tex
tabel staat nu mooi na referenties

\title{A cross-benchmark comparison of Learning to Rank methods}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

@@

\section{Introduction}
Ranking is a core problem in the field of information retrieval. The ranking task in information retrieval entails the ranking of candidate documents according to their relevance for a given query. Ranking has become a vital part of web search, where commercial search engines help users find their need in the extremely large collection of the World Wide Web. One can find useful applications of ranking in many application domains outside web search as well. For example, it plays a vital role in amongst others: automatic document summarisation, machine translation, drug discovery and in determining the ideal order of maintenance operations \cite{Rudin2009}. In addition, the ranking task has been argued to be more fitting to recommender systems than regression-based rating prediction on a continuous scale \cite{Adomavicius2005,McNee2006}.\\

Research in the field of ranking models has for a long time been based on manually designed ranking functions, such as the well-known BM25 model \cite{Robertson1994}. Luhn \cite{Luhn1957} was the first to propose a model that assigned relevance scores to documents given a query back in 1957. The increasing amounts of potential training data have recently made it possible to leverage machine learning methods to obtain more effective models. Learning to Rank is the relatively new research area that covers the use of machine learning models for the ranking task.\\

In recent years, several learning to rank benchmark datasets have been proposed that enable comparison of the performance of different learning to rank methods. Well-known benchmark datasets include the \emph{Yahoo! Learning to Rank Challenge} dataset \cite{Chapelle2011a}, the Yandex Internet Mathematics competition\footnote{http://imat-relpred.yandex.ru/en/}, and the LETOR dataset \cite{Qin2010} that was published by Microsoft Research.\\

No agreement exists between authors in the learning to rank field on the benchmark sets used for model evaluation. Comparing ranking performance of learning to rank methods is largely hindered by the existence of this variety of evaluation datasets and the lack of a \emph{de facto} standard way of benchmarking new models.

\section{Problem Statement \& Research Question}
\label{chap:cross_comparison}
Because the learning to rank methods evaluated differs between benchmarks, no single benchmark comparison can be regarded as a conclusive argument on which learning to rank method is most accurate.\\

Several studies make a small start in considering learning to rank methods performance over multiple benchmark datasets. Gomes et al. \cite{Gomes2013} analysed ranking accuracy of a set of models on both LETOR 3.0 and LETOR 4.0. Busa-Fekete et al. \cite{Busa-Fekete2013} compared the accuracy of a small set of models over the LETOR 4.0 datasets, both MSLR datasets, both Yahoo! Learning to Rank Challenge datasets and the OHSUMED dataset from LETOR 3.0. To my knowledge, no structured meta-analysis on ranking accuracy has been conducted where evaluation results on several benchmark collections are taken into account. With a meta-analysis we will compare the performance of learning to rank methods across the learning to rank benchmark datasets described in foregoing sections.

\section{Collecting Evaluation Results}
\label{sec:collecting_evaluation_results}
With a literature review we will collect evaluation results on the datasets/collections. The following list presents an overview of the benchmark collections taken into account in the meta-analysis:
\begin{itemize}\itemsep0em
\item LETOR 2.0
\item LETOR 3.0
\item LETOR 4.0
\item Yahoo! Learning to Rank Challenge
\item Yandex Internet Mathematics Competition 2009
\item MSLR-web10/30k
\item WCL2R
\item AOL
\end{itemize}

@@

\section{Comparison Methodology}
The LETOR 3.0 paper \cite{Qin2010} states that it may differ between datasets what the most accurate ranking methods are. To evaluate the overall performance of learning to rank methods over the multiple datasets in the LETOR 3.0 collections, Qin et al. \cite{Qin2010} proposed a measure called \emph{winning number} as the number of other algorithms that an algorithm can beat over the set of datasets. Formally the winning number measure is defined as\\

@@

\section{Evaluation Results Found in Literature}
Table \ref{tab:ltr_methods_used} gives an overview of the learning to rank methods for which evaluation results were found for one or more of the benchmark datasets listed in section~\ref{sec:collecting_evaluation_results} through the literature review process also described in section~\ref{sec:collecting_evaluation_results}. Occurrences of L2, L3 and L4 in Table \ref{tab:ltr_methods_used} imply that these algorithms are evaluated as official LETOR 2.0, LETOR 3.0 and LETOR 4.0 baselines respectively.\\

@@

\begin{table*}[!h!p]

@@

\section{Results \& Discussion}
The following subsections provide the performance of learning to rank methods in terms of Normalised Winning Number for NDCG@3, NDCG@5, NDCG@10 and MAP. Performance of the learning to rank methods is plotted with Normalised Winning Number on the vertical axis and the number of datasets on which the method has been evaluated on the horizontal axis. The further to the right, the more certain we can be about the performance of the learning to rank method. The methods for which it holds that there is no other method that has 1) a higher Normalised Winning Number and 2) a higher number datasets evaluated, are identified as the best performing methods and are labelled with the name of the method.

\subsection{NDCG@3}
Figure \ref{fig:normalised_winning_number_ndcg3} shows the performance of learning to rank methods for the NDCG@3 metric. Table \ref{tab:raw_data_norm_winnum_ndcg3} in Appendix \ref{app:norm_winnum_ndcg3} provides the raw Normalised Winning Number data for the learning to rank methods for which NDCG@3 evaluation results were available.\\

@@

\subsection{NDCG@5}
Figure \ref{fig:normalised_winning_number_ndcg5} shows the performance of learning to rank methods for the NDCG@5 metric. Table \ref{tab:raw_data_norm_winnum_ndcg5} in Appendix \ref{app:norm_winnum_ndcg5} provides the raw Normalised Winning Number data for the learning to rank methods.\\

@@

\subsection{NDCG@10}
Figure \ref{fig:normalised_winning_number_ndcg10} shows the performance of learning to rank methods for the NDCG@10 metric. Table \ref{tab:raw_data_norm_winnum_ndcg10} in Appendix \ref{app:norm_winnum_ndcg10} provides the raw Normalised Winning Number data for the learning to rank methods.\\

\begin{figure*}[!htp]
\includegraphics[scale=0.285]{gfx/ndcg10_winnum}
\caption{NDCG@10 comparison of learning to rank methods}
\label{fig:normalised_winning_number_ndcg10}
\end{figure*}

@@

\subsection{MAP}
Figure \ref{fig:normalised_winning_number_map} shows the performance of learning to rank methods for the MAP metric. Table \ref{tab:raw_data_norm_winnum_map} in Appendix \ref{app:norm_winnum_map} provides the raw Normalised Winning Number data for the learning to rank methods.\\

\begin{figure*}[!htp]
\includegraphics[scale=0.285]{gfx/map_winnum}
\caption{MAP comparison of learning to rank methods}
\label{fig:normalised_winning_number_map}
\end{figure*}

@@

\subsection{Cross-metric}
Figure \ref{fig:normalised_winning_number_all} shows the Normalised Winning Number as function of Ideal Winning Number for the methods described in Table \ref{tab:ltr_methods_used}. Table \ref{tab:raw_data_norm_winnum_all} in Appendix \ref{app:norm_winnum_all} provide the raw data plotted in Figure \ref{fig:normalised_winning_number_all}.\\

\begin{figure*}[!htp]
\includegraphics[scale=0.33]{gfx/combined_normalized_winnum}
\caption{Cross-benchmark comparison of learning to rank methods}
\label{fig:normalised_winning_number_all}
\end{figure*}

@@

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{Bibliography}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
\appendix
\section{Cross-Comparison Raw Data}
\label{app:raw_data}
\onecolumn
\begin{longtable}{@{}lrrrrrrrrrrrrrrrr@{}}\toprule

>>>>

\title{A Cross-Benchmark Comparison of Learning to Rank Methods}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

@@

\section{Introduction}
Ranking is a core problem in the field of information retrieval. The ranking task in information retrieval entails the ranking of candidate documents according to their relevance to a given query. Ranking has become a vital part of web search, where commercial search engines help users find their need in the extremely large collection of the World Wide Web. One can find useful applications of ranking in many application domains outside web search as well. For example, ranking plays a vital role in automatic text summarisation, machine translation, drug discovery and in determining the ideal order of maintenance operations \cite{Rudin2009}. In addition, the ranking task has been argued to be a better fit for recommender systems compared to the regression task on a continuous scale \cite{Adomavicius2005,McNee2006}.\\

Research in the field of ranking models has for a long time been based on manually designed ranking functions, such as the well-known BM25 model \cite{Robertson1994}. Luhn \cite{Luhn1957} was the first to propose a model that assigned relevance scores to documents given a query back in 1957. The increasing amounts of potential training data have recently made it possible to leverage machine learning methods to obtain more effective ranking models. Learning to rank is the relatively new research area that covers the use of machine learning models for the ranking task.\\

In recent years, several learning to rank benchmark datasets have been proposed with the aim of enabling comparison of the performance of different learning to rank methods. Well-known benchmark datasets in the learning to rank field include the \emph{Yahoo! Learning to Rank Challenge} dataset \cite{Chapelle2011a}, the Yandex Internet Mathematics competition\footnote{http://imat-relpred.yandex.ru/en/}, the LETOR dataset \cite{Qin2010}, and LETOR's successor the MSLR (Microsoft Learning to Rank) datasets.\\

No agreement exists between authors in the learning to rank field on the benchmark sets used for model evaluation. Comparing ranking performance of learning to rank methods is largely hindered by this lack of a \emph{de facto} standard way of benchmarking new models.

Several studies make a small start in considering learning to rank methods performance over multiple benchmark datasets. Gomes et al. \cite{Gomes2013} analysed ranking accuracy of a set of models on both LETOR 3.0 and LETOR 4.0. Busa-Fekete et al. \cite{Busa-Fekete2013} compared the accuracy of a small set of models over the LETOR 4.0 datasets, both MSLR datasets, both Yahoo! Learning to Rank Challenge datasets and one of the datasets from LETOR 3.0.\\

To our knowledge, no structured meta-analysis on ranking accuracy has been conducted where evaluation results on several benchmark collections are taken into account. In this paper we will perform a meta-analysis with the aim of comparing the ranking accuracy of learning to rank methods.

\section{Collecting Evaluation Results}

\subsection{Evaluation Results Collection Methodology}
\label{sec:collecting_evaluation_results}
With a literature review we will collect evaluation results on the datasets/collections. The following list presents an overview of the benchmark collections taken into account in the meta-analysis:
\begin{itemize}\itemsep0em
\item LETOR 2.0
\item LETOR 3.0
\item LETOR 4.0
\item Yahoo! Learning to Rank Challenge
\item Yandex Internet Mathematics Competition 2009
\item MSLR-web10/30k
\item WCL2R
\item AOL
\end{itemize}

@@

\subsection{Comparison Methodology of Learning to Rank Methods}
The LETOR 3.0 paper \cite{Qin2010} states that it may differ between datasets what the most accurate ranking methods are. To evaluate the overall performance of learning to rank methods over the multiple datasets in the LETOR 3.0 collections, Qin et al. \cite{Qin2010} proposed a measure called \emph{winning number} as the number of other algorithms that an algorithm can beat over the set of datasets. Formally the winning number measure is defined as\\

@@

\section{Results \& Discussion}
\subsection{Collection of Evaluation Results}
Table \ref{tab:ltr_methods_used} gives an overview of the learning to rank methods for which evaluation results were found for one or more of the benchmark datasets listed in section~\ref{sec:collecting_evaluation_results} through the literature review process also described in section~\ref{sec:collecting_evaluation_results}. Occurrences of L2, L3 and L4 in Table \ref{tab:ltr_methods_used} imply that these algorithms are evaluated as official LETOR 2.0, LETOR 3.0 and LETOR 4.0 baselines respectively.\\

@@

\begin{table*}

@@

\subsection{Comparison of Learning to Rank models}
The following subsections provide the performance of learning to rank methods in terms of Normalised Winning Number for NDCG@3, NDCG@5, NDCG@10 and MAP. Performance of the learning to rank methods is plotted with Normalised Winning Number on the vertical axis and the number of datasets on which the method has been evaluated on the horizontal axis. The further to the right, the more certain we can be about the performance of the learning to rank method. The methods for which it holds that there is no other method that has 1) a higher Normalised Winning Number and 2) a higher number datasets evaluated, are identified as the best performing methods and are labelled with the name of the method.

\subsubsection{NDCG@3}
Figure \ref{fig:normalised_winning_number_ndcg3} shows the performance of learning to rank methods for the NDCG@3 metric. Table \ref{tab:raw_data_norm_winnum_ndcg3} in Appendix \ref{app:norm_winnum_ndcg3} provides the raw Normalised Winning Number data for the learning to rank methods for which NDCG@3 evaluation results were available.\\

@@

\subsubsection{NDCG@5}
Figure \ref{fig:normalised_winning_number_ndcg5} shows the performance of learning to rank methods for the NDCG@5 metric. Table \ref{tab:raw_data_norm_winnum_ndcg5} in Appendix \ref{app:norm_winnum_ndcg5} provides the raw Normalised Winning Number data for the learning to rank methods.\\

@@

\subsubsection{NDCG@10}
Figure \ref{fig:normalised_winning_number_ndcg10} shows the performance of learning to rank methods for the NDCG@10 metric. Table \ref{tab:raw_data_norm_winnum_ndcg10} in Appendix \ref{app:norm_winnum_ndcg10} provides the raw Normalised Winning Number data for the learning to rank methods.\\

\begin{figure*}
\includegraphics[scale=0.285]{gfx/ndcg10_winnum}
\caption{NDCG@10 comparison of learning to rank methods}
\label{fig:normalised_winning_number_ndcg10}
\end{figure*}

@@

\subsubsection{MAP}
Figure \ref{fig:normalised_winning_number_map} shows the performance of learning to rank methods for the MAP metric. Table \ref{tab:raw_data_norm_winnum_map} in Appendix \ref{app:norm_winnum_map} provides the raw Normalised Winning Number data for the learning to rank methods.\\

\begin{figure*}
\includegraphics[scale=0.285]{gfx/map_winnum}
\caption{MAP comparison of learning to rank methods}
\label{fig:normalised_winning_number_map}
\end{figure*}

@@

\subsubsection{Cross-metric}
Figure \ref{fig:normalised_winning_number_all} shows the Normalised Winning Number as function of Ideal Winning Number for the methods described in Table \ref{tab:ltr_methods_used}. Table \ref{tab:raw_data_norm_winnum_all} in Appendix \ref{app:norm_winnum_all} provide the raw data plotted in Figure \ref{fig:normalised_winning_number_all}.\\

\begin{figure*}
\includegraphics[scale=0.33]{gfx/combined_normalized_winnum}
\caption{Cross-benchmark comparison of learning to rank methods}
\label{fig:normalised_winning_number_all}
\end{figure*}

@@

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{Bibliography}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
\onecolumn
\clearpage
\newpage
\appendix
\section{Cross-Comparison Raw Data}
\label{app:raw_data}

\begin{longtable}[!h]{@{}lrrrrrrrrrrrrrrrr@{}}\toprule
